HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
www

In order to validate the HUME metric, we ran an annotation experiment with one source language (English), and four 
target languages (Czech, German, Polish and Romanian), using text from the public health domain. We are 
particularly interested in this domain since our ultimate goal is to provide high-quality translations of health
information for speakers of languages other than English, and in this domain accurate transfer of meaning is
paramount.

Our annotation experiment sought to address the following questions:
\begin{compactitem}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{compactitem}

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair.

@@

Looking more closely at the areas of disagreement, we see that for the Polish structural nodes, the 
proportion of As was quite different between the two annotators (53\% vs. 71\%), whereas for other
languages the annotators agree in the proportions. We believe that this was because one of the Polish
annotators did not fully understand the guidelines for structural nodes, and percolated
errors up the tree, creating more Bs. For the German lexical nodes, and Czech structural nodes, where
Kappa is also around 0.3, the proportion of such nodes being marked as ``correct'' is relatively 
high, meaning that the class distribution is more skewed, so the expected agreement used in the
Kappa calculation is high, lowering Kappa. Essentially, the annotation problem is harder when the classes
are more skewed. Finally we note some evidence of domain-specific disagreements, for instance the German
MT system normally translated ``review'' (as in ``systematic review'' -- a frequent term in the 
Cochrane texts) as ``\"uberpr\"ufung'', which 
one annotator marked correct, and the other (a Cochrane employee)  as incorrect.

>>>>

In order to validate the HUME metric, we ran an annotation experiment with one source language (English), and four 
target languages (Czech, German, Polish and Romanian), using text from the public health domain.
The domain is particularly suitable for experimenting on MT evaluation, as being able to determine
whether the translation accurately conveys the same information as the source is here paramount.

%particularly interested in this domain since our ultimate goal is to provide high-quality translations of health
%information for speakers of languages other than English, and in this domain accurate transfer of meaning is
%paramount.

The experiment seeks to address two questions:

\begin{compactitem}
\item Can HUME be annotated quickly and reliably, and does the reliability still hold for longer sentences?
\item Can HUME capture translation issues that other annotation schemes (such as
adequacy judgements and HMEANT)
cannot?
%\item What can HUME annotation tell us about the strengths and weaknesses of MT?
%\bh{Maybe we should remove the third one, we
%probably don't address it in this paper}
\end{compactitem}

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair\oa{I think we should probably
  say how much in each.}.

@@

\XXX{Discussion of the disagreements}

\begin{compactitem}
  \item German has low overall proportion of orange annotation (1.2\% compared with 4.5-8.6)
  \item German annotators give a lot of green (so skewed classes, high expected agreement), but 
        differ more significantly on what should be green. 
  \item For Polish, big difference in number of As (2000 vs 1500) given by each annotator
  \item For Czech structural, both annotators give higher proportion of As, raising the expected agreement.
\end{compactitem}
